Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-13 paper/ms.tex
update ms

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips in CQVs can happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
entire class of star is probably part of the same phenomenon, we
therefore generally discard the ``spot-only'' scenario.

@@

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the degree of observed periodicity,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale typically quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

To correctly identify local minima near the edges of the phased light
curve, which usually would cover phases $\phi \in [ 0,1 ]$, we
performed the entire procedure over a phase-folded light curve
spanning $\phi \in [-1,2 ]$, by duplicating and concatenating the
ordinary phase-folded light curve.  The free parameters we adopted
throughout this analysis procedure, for instance the maximum number of
spline knots per cycle, and how large and wide of a local minimum to
consider a ``true dip'', were chosen during testing based on their
ability to correctly re-identify a large fraction ($>$90\%) of known
CQVs, while also being able to consistently reject common false
positives such as rapidly rotating spot-induced variability and
typical eclipsing binaries.

@@

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  In the sectors for which
we performed this analysis, we found that ``summary'' sheets were
generated for approximately 10\% of the 20\,000 120-second targets in
a given sector.  We then manually reviewed each summary sheet, and
visually labelled each star based on its morphology (including e.g.,
eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
were observed in multiple sectors had their light curves stitched
together and analyzed for a more accurate period determination.

@@

We visually assessed whether the objects found using the dip-counting
(Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) techniques were consistent with
expectations for CQVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if at least
one TESS sector showed what we viewed as the unambiguous signatures of
the class (short period; at least three dips or else otherwise
oddly-shaped dips; relative stability over a timescale of 30\,days).
We independently noted stars that we thought could be CQVs, but that
were more ambiguous.

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We specifically omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE 3-4, but due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we statically sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality, and youth, of that group.  The yield
in Sco-Cen is not particularly surprising, since Sco-Cen contains the
majority of pre-main-sequence stars in the solar neighborhood.
However, given the $\lesssim$$10\%$ completeness of TESS beyond
100\,pc, there are probably many more CQVs that remain to be
discovered in Sco-Cen.

@@

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  However both do seem to
clearly show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  For instance,
both were noted by \citet{2021ApJ...917...23K} as being in the
``diffuse'' population of $<$50\,Myr stars near the Sun.

@@

The upper age limit for CQVs may even pass 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
primarily rests on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades and younger than the 400\,Myr Ursa Major
moving group.  The formal BANYAN-$\Sigma$ membership probability is
however somewhat low, perhaps due to the missing radial velocity.
This could be relatively easily resolved by acquiring even a
medium-resolution spectrum.  An independent assessment of the group's
kinematics using Gaia data, and its rotation sequence using TESS,
could lend further credence in such an analysis.

@@

Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
the CQV phenomenon in one sector, and marginal or non-existent signs
in the other.  While there is subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  Based on the fraction of sources overall that ``turned off'',
the observed shape evolution implies that CQVs have a duty cycle of
$\approx$75\%.  This type of correction is likely worth including in
population-level estimates of how intrinsically common CQVs are in the
low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.

@@

Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
The star was observed at 120-second cadence whenever it was observable
by TESS.  We binned the light curve to 15-minute intervals for visual
clarity, and required at least one (120-second cadence) flux
measurement per bin.  Points more than 2.5$\sigma$ above the median
are drawn in gray, also for visual clarity.  Missing data are not
drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
successive TESS orbits spanning half a lunar month each.
Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
same data, split into similar intervals:
the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
The river plots are slightly more processed:
a maximum-likelihood two-harmonic sinusoid has been independently fitted and
subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
data in order to accentuate any changes in the dip timing and structure.

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.   However, in detail, a period shift
of $\pm$1\,minute would yield major phase drifts over the baseline;
that time interval corresponds to roughly 1/1000$^{\rm th}$ of a
period, and we have observed 1500 cycles.  By visually fine-tuning
over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
which seems to track certain features in the LP 12-502 light curve
well over the entire dataset.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two intricately structured dip complexes, plus a small leading dip.
The single leading dip is present at the same phase as in cycles 0-64,
and is therefore likely to be the same struture.  Along a similar line
of logic, it seems plausible that the first ``dip complex'' during
cycles 248-264 represents an evolution of the initial complex seen
during cycles 0-64, though with greatly reduced depth.  During cycles
266-310, an additional local minimum develops between the two
complexes; this feature is best visualized on the river plots
(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period below.

@@

{\sc State-switches reveal dip independence}---The state-switches seen
in cycles 1233-1247 and 299-315 confirm that dips can disappear in
less than one cycle, a point which has been previously appreciated
\citep{2017AJ....153..152S}.  What is new in these particular changes
is that the morphology changes show that the dips can be {\it
independent} and {\it additive}.  For example, throughout cycles
1233-1264, there are three local minima between phases of 0 and 0.3.
They all have identical ingress times.  The shape change during the
transition implies that the leading dip that ``turned off'' (reduced
its depth and duration), while the trailing two dips remained fixed.
This is visible in Figure~\ref{fig:lp}.
In other words, the structures producing these dips are independent to
the degree that one can undergo a severe change while the others
remain essentially identical.  The state switches during cycles
248-264 and 299-315 share the same characteristic: it is always the
{\it leading} dip of a complex that ``switches off'', leaving the
(fixed-depth) trailing dips in its wake.

{\sc Slow growth; rapid death}---Although there are a few instances in
which we observe dips switch off over less than one cycle, dip
growth seems to happen more slowly.  For instance, the dip that grows
between phase 0 and 0.1 between cycles 260-290 begins to become
visible around BTJD 1993.2, and growths in depth by about 2\% over
about six cycles, to become easily detectable by eye by BTJD 1997.7.
The evolution of this particular dip is most clear in the river plots.
The evolution of the latter dip group in cycles 1410-1481 is another
example of this slow mode of dip growth.

@@

Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
for our CQV catalog, and compares them against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
and age includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
\citealt{2018A&A...619A.177B}).  We found no obvious morphology
differences between the two classes.  In terms of their rotation,
relative to the Pleiades, the CQVs are among the more rapidly rotating
half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
despite our search extending to $T$$=$16, is a consequence of the
120-second selection function, not detection sensitivity.

@@

Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as a
whole show any preference for sharper ingresses, or sharper egresses.
In some cases (e.g. TIC~425933644), the continuum itself is not
well-defined, and so the meaning of ``ingress'' and ``egress'' are not
clear.  In others, such as Sector~36 of TIC~89463560, there is a
single clear sharp ingress with an exponential egress, which could be
directly fit using e.g.~a model analogous to those used for exocomets
\citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
in such models would be the exponential decay time- and therefore
length-scale, as well as the impact parameter and the inferred transit
depth (and its implications for the equivalent ``radius'' of the
transiting cloud).  Although we briefly explored such models, it
quickly became clear that careful modeling of sources such as LP
12-502 merits its own in-depth study.  Connections could likely also
be made to the toroidal geometries that can be produced by outflowing
atmospheres of transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

%TODO: improve this to make it less jargony

The difference between the prominence and dust clump scenarios is
essentially only in whether the occulting material of interest is
neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
condition of ideal rigid field magnetohydrodynamics, the tendency of
both to become trapped at the corotation radius in the equatorial
plane is tied to how of the four relevant forces (gravity, Lorentz,
inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm cr}$
\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
is only relevant in this formulation of the system in that we must
have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for closed
loops to exist that can support prominences
\citep{2019MNRAS.482.2853J} {\bf lgb todo: verify \& de-jargonify!}.
In detail however, whether such magnetic fixed points lie in the
equatorial plane, or elsewhere, depends on the star's magnetic field
geometry \citep{2023MNRAS.518.4734S}.

@@

One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
which only lasts for half of any given cycle.  TIC~206544316 (Sector
2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
TIC~312410638 (Sector 38) seem to show essentially the same tendency.

>>>>

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips in CQVs can happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
entire class of star is probably part of the same phenomenon, we
therefore discard the ``spot-only'' scenario.

@@

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the degree of observed periodicity,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale often quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

To identify local minima near the edges of the phased light
curve, which usually would cover phases $\phi \in [ 0,1 ]$, we
performed the entire procedure over a phase-folded light curve
spanning $\phi \in [-1,2 ]$, by duplicating and concatenating the
ordinary phase-folded light curve.  The free parameters we adopted
throughout this analysis procedure, for instance the maximum number of
spline knots per cycle, and how large and wide of a local minimum to
consider a ``true dip'', were chosen during testing based on their
ability to correctly re-identify a large fraction ($>$90\%) of known
CQVs, while also being able to consistently reject common false
positives such as rapidly rotating spot-induced variability and
typical eclipsing binaries.

@@

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  In the sectors for which
we performed this analysis, we found that ``summary'' sheets were
generated for $\approx$10\% of the 20\,000 120-second targets in
a given sector.  We then manually reviewed each summary sheet, and
visually labelled each star based on its morphology (including e.g.,
eclipsing binary, CQV, RS CVn, or cataclysmic variable).  CQVs that
were observed in multiple sectors had their light curves stitched
together and analyzed for a more accurate period determination.

@@

We assessed whether the objects found using the dip-counting
(Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) techniques were consistent with
expectations for CQVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if at least
one TESS sector showed what we viewed as the unambiguous signatures of
the class (short period; at least three dips or else otherwise
oddly-shaped dips; relative stability over a timescale of 30\,days).
We independently noted stars that we thought could be CQVs, but that
were more ambiguous.

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE 3-4, but due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality, and youth, of that group.  The yield
in Sco-Cen is not surprising, since Sco-Cen contains the
majority of pre-main-sequence stars in the solar neighborhood.
However, given the $\lesssim$$10\%$ completeness of TESS beyond
100\,pc, there are probably many more CQVs that remain to be
discovered in Sco-Cen.

@@

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  However both do seem to
show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  For instance,
both were noted by \citet{2021ApJ...917...23K} as being in the
``diffuse'' population of $<$50\,Myr stars near the Sun.

@@

The upper age limit for CQVs may even pass 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
is based on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades and younger than the 400\,Myr Ursa Major
moving group.  The formal BANYAN-$\Sigma$ membership probability is
however somewhat low, perhaps due to the missing radial velocity.
This could be resolved by acquiring even a
medium-resolution spectrum.  An independent assessment of the group's
kinematics using Gaia data, and its rotation sequence using TESS,
could lend further credence in such an analysis.

@@

Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
the CQV phenomenon in one sector, and marginal or non-existent signs
in the other.  While there is subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  Based on the fraction of sources overall that ``turned off'',
the observed shape evolution implies that CQVs have a duty cycle of
$\approx$75\%.  This type of correction is worth including in
population-level estimates of how intrinsically common CQVs are in the
low-mass stellar population \citep[e.g.][]{2022AJ....163..144G}.

@@

Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
The star was observed at 120-second cadence whenever it was observable
by TESS.  We binned the light curve to 15-minute intervals for visual
clarity, and required at least one (120-second cadence) flux
measurement per bin.  Points more than 2.5$\sigma$ above the median
are drawn in gray, also for visual clarity.  Missing data are not
drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
successive TESS orbits spanning half a lunar month each.
Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
same data, split into similar intervals:
the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
The river plots are subject to one additional processing step:
we fitted and subtracted a maximum-likelihood two-harmonic sinusoid
independently from the Sector 18-19 data, 25-26 data, and 53, 58, and 59 data
in order to accentuate changes in the dip timing and structure.

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.   However, in detail, a period shift
of $\pm$1\,minute would yield major phase drifts over the baseline;
that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
period, and we have observed 1500 cycles.  By fine-tuning
over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
which seems to track certain features in the LP 12-502 light curve
well over the entire dataset.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two highly structured dip complexes, plus a small leading dip.
The single leading dip is present at the same phase as in cycles 0-64,
and is therefore likely to be the same struture.  Along a similar line
of logic, it seems plausible that the first ``dip complex'' during
cycles 248-264 represents an evolution of the initial complex seen
during cycles 0-64, though with reduced depth.  During cycles
266-310, an additional local minimum develops between the two
complexes; this feature is best visualized on the river plots
(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period below.

@@

{\sc State-switches reveal dip independence}---The state-switches seen
in cycles 1233-1247 and 299-315 confirm that dips can disappear in
less than one cycle, a point which has been previously appreciated
\citep{2017AJ....153..152S}.  What is new in these particular changes
is that the morphology changes show that the dips can be {\it
independent} and {\it additive}.  For example, throughout cycles
1233-1264, there are three local minima between phases of 0 and 0.3.
They all have identical ingress times.  The shape change during the
transition implies that the leading dip that ``turned off'' (reduced
its depth and duration), while the trailing two dips remained fixed.
This is visible in Figure~\ref{fig:lp}.
In other words, the structures producing these dips are independent to
the degree that one can undergo a severe change while the others
remain identical.  The state switches during cycles
248-264 and 299-315 share the same characteristic: it is always the
{\it leading} dip of a complex that ``switches off'', leaving the
(fixed-depth) trailing dips in its wake.

{\sc Slow growth; rapid death}---Although there are a few instances in
which we observe dips switch off over less than one cycle, dip
growth seems to happen more slowly.  For instance, the dip that grows
between phase 0 and 0.1 between cycles 260-290 begins to become
visible around BTJD 1993.2, and growths in depth by about 2\% over
about six cycles, to become visible by eye by BTJD 1997.7.
The evolution of this particular dip is most clear in the river plots.
The evolution of the latter dip group in cycles 1410-1481 is another
example of this slow mode of dip growth.

@@

Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
for our CQV catalog, and compares them against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
and age includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
\citealt{2018A&A...619A.177B}).  We found no obvious morphology
differences between the two classes, which is somewhat surprising 
if the two stellar classes tend to have distinct field topologies
\citep{2009A&A...496..787R}.  In terms of their rotation rates,
relative to the Pleiades, the CQVs are among the more rapidly rotating
half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
despite our search extending to $T$$=$16, is a consequence of the
120-second selection function, not detection sensitivity.

@@

Examining Figure~\ref{fig:cqvs}, it is not obvious whether CQVs as a
whole show any preference for sharper ingresses, or sharper egresses.
In some cases (e.g. TIC~425933644), the continuum itself is not
well-defined, and so the meaning of ``ingress'' and ``egress'' are not
clear.  In others, such as Sector~36 of TIC~89463560, there is a
single clear sharp ingress with an exponential egress, which could be
fitted using e.g.~a model analogous to those used for exocomets
\citep[e.g.][]{2019A&A...625L..13Z}.  The main quantities of interest
in such models would be the exponential decay time- and therefore
length-scale, as well as the impact parameter and the inferred transit
depth (and its implications for the equivalent ``radius'' of the
transiting cloud).  We briefly explored such models, until it
became clear that careful modeling of sources such as LP
12-502 merits its own in-depth study.  Connections could likely also
be made to the toroidal geometries that can be produced by outflowing
atmospheres of transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

The key difference between the prominence and dust clump scenarios is
in whether the occulting material of interest is
neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
condition of ideal rigid field magnetohydrodynamics, the tendency of
both to become trapped at the corotation radius in the equatorial
plane is tied to how of the four relevant forces (gravity, Lorentz,
inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm cr}$
\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
is only relevant in this formulation of the system in that we must
have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for closed
loops to exist that can support prominences
\citep{2019MNRAS.482.2853J}.  In detail however, the locations of such
magnetic fixed points depends on the star's magnetic field topology
\citep{2023MNRAS.518.4734S}.

@@

One set of CQVs shows ``CQV behavior'' (some form of dip complex), but
which only lasts for half of any given cycle.  TIC~206544316 (Sector
2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
TIC~312410638 (Sector 38) seem to show the same tendency.
